Growing libraries of concepts with wake-sleep program induction

### 2018-07-20 talk.tex
labels for sections

@@

\begin{frame}[t]{EC}
  \includegraphics[width = 11cm]{figures/animation/EC.eps}
\end{frame}
\begin{frame}[t]{DC}
  \includegraphics[width = 11cm]{figures/animation/DC.eps}
\end{frame}
\begin{frame}[t]{Wake}
  \includegraphics[width = 11cm]{figures/animation/Wake.eps}
\end{frame}
\begin{frame}[t]{Sleep-G}
  \includegraphics[width = 11cm]{figures/animation/Sleep-G.eps}
\end{frame}
\begin{frame}[t]{Sleep-R-1}
  \includegraphics[width = 11cm]{figures/animation/Sleep-R-1.eps}
\end{frame}
\begin{frame}[t]{Sleep-R-2}
  \includegraphics[width = 11cm]{figures/animation/Sleep-R-2.eps}

@@

\begin{frame}{DSL: Library of concepts}
\includegraphics[width = 11cm]{3DSL.png}
\end{frame}

\begin{frame}{DSL learning as Bayesian inference}
  \centering

\begin{tikzpicture}[scale=2,line width=1.5mm]

  \node[latent,scale=2,align=center] at (3.5,3) (dx){DSL};
  \node[ellipse,fill=white,draw=black,inner sep=1pt,
minimum size=20pt, font=\fontsize{10}{10}\selectfont, node distance=1,scale=2] at ([xshift=2cm]dx) (zp){program};
  \node[obs,scale=2] at ([xshift=2cm]zp) (xp) {task};
  \plate {}{(zp)(xp)}{};
%  \node[align = center] at ([yshift = -1.2cm,xshift = 1cm]xp.east) {(b) \\recognition model};
  %% \draw [->,red] (xp.south) to[out = -90,in = -90] node(nn){} (zp.south);
%  \draw [->,red] (tx.west) -- (zp.east);
  \draw [->] (dx.east) -- (zp.west);
  \draw [->] (zp.east) -- (xp.west);

  \end{tikzpicture}
 %%  \begin{tikzpicture}
 %%    \node[latent,align=center] (g) {DSL: \\concept library};
 %%    \node[latent,below = of g,xshift = -2cm] (e1) {$\text{program}_1$};
 %%    \node[latent,below = of g,xshift = 0cm] (e2) {$\text{program}_2$};
 %% \node[latent,below = of g,xshift = 2cm] (e3) {$\text{program}_3$};
 %%    \node[obs,below = of e1] (x1) {$\text{task}_1$};
 %%    \node[obs,below = of e2] (x2) {$\text{task}_2$};
 %%    \node[obs,below = of e3] (x3) {$\text{task}_3$};
 %%    \edge {g} {e1,e2,e3};
 %%    \edge {e1} {x1};
 %%    \edge {e2} {x2};
 %%    \edge {e3} {x3};
 %%  \end{tikzpicture}

@@

\begin{frame}{Amortized program inference}

  \includegraphics[width = 9cm]{rm.png}

  \begin{itemize}
  \item $\mathcal{D}$: DSL
  \item $p_n$: program
  \item $x_n$: task
  \item $Q$: Recognition model
    \end{itemize}

>>>>

\newcommand\Wider[2][3em]{%
\makebox[\linewidth][c]{%
  \begin{minipage}{\dimexpr\textwidth+#1\relax}
  \raggedright#2
  \end{minipage}%
  }%
}

@@

@@

\begin{frame}{DSL: Library of concepts}
\Wider[5.4em]{
  \renewcommand\code\texttt
  \renewcommand\codechar[1]{\texttt{"#1"}}
  \newcommand{\helpSize}{0.25cm}
  \footnotesize\begin{tabular}{cc}
    \toprule
Tasks and     \pop{Programs} & DSL\\
    \midrule
      \begin{tabular}{cc}
        \begin{tabular}{c}
          \code{[7\, 2\, 3]}$\to$\code{[7\, 3]}         \\
          \code{[1\, 2\, 3\, 4]}$\to$\code{[3\, 4]} \\
          \code{[4\, 3\, 2\, 1]}$\to$\code{[4\, 3]} \\
          \pop{\code{$f(\ell) = $}\code{($f_1$ $\ell$ ($\lambda$ (x)}}\\
          \hspace{1.15cm}\pop{\code{(> x 2)))}}       \\
          \\
          \\
          \code{[2\, 7\, 8\, 1]}$\to $\code{8}               \\
          \hspace{0.15cm}\code{[3\, 19\, 14]}$\to $\code{19}                \\
          \pop{\code{$f(\ell) = $}\code{($f_2$ $\ell$)}}
        \end{tabular}
        &
        \hspace{-0.3cm}\begin{tabular}{c}
          \code{[7\, 3]}$\to $\code{False}                              \\
          \hspace{0.3cm}\code{[3]}$\to $\code{False}                    \\
          \hspace{-0.3cm}\code{[9\, 0\, 0]}$\to $\code{True\phantom{e}} \\
          \hspace{0.3cm}\code{[0]}$\to $\code{True\phantom{e}}                        \\
          \hspace{-0.3cm}\code{[0\, 7\, 3]}$\to $\code{True\phantom{e}}                \\
          \pop{\code{$f(\ell) = $}\code{($f_3$ $\ell$ 0)}}
        \end{tabular}
      \end{tabular}
    &
    \begin{tabular}{l}
      \popp{$f_0(\ell,$\code{r}$) \,=\, $\code{(foldr r $\ell$ cons)}}\\
      \hspace{\helpSize}($f_0$: \emph{Append lists }\code{r}\emph{ and  $\ell$})\\
      \popp{$f_1(\ell,$\code{p}$) \,=\, $\code{(foldr $\ell$ nil ($\lambda$ (x a)}}\\
      \hspace{0.5cm}\popp{\code{(if (p x) (cons x a) a)))}}\\
      \hspace{\helpSize}($f_1$: \emph{Higher-order filter function})\\
      %(lambda (fold $0 0 (lambda (lambda (if (gt? $0 $1) $0 $1)))))
      \popp{$f_2(\ell) \,=\, $\code{(foldr $\ell$ 0 ($\lambda$ (x a)}}\\
      \popp{\phantom{$f_2(\ell) \,=\, $}\code{(if (> a x) a x)))}}\\
      \hspace{\helpSize}($f_2$: \emph{Maximum element in list $\ell$})\\
      \popp{$f_3(\ell,$\code{k}$) \,=\, $\code{(foldr $\ell$ (is-nil $\ell$)}}\\
      \phantom{$f_1(\ell,$}
      \popp{\code{($\lambda$ (x a) (if a a (= k x))))}}\\
      \hspace{\helpSize}($f_2$: \emph{Whether $\ell$ contains }\code{k})\\
    \end{tabular}
  \\\bottomrule
  \end{tabular}
}
\end{frame}

\begin{frame}[t]{DSL learning as Bayesian inference}
  \includegraphics[width = 11cm]{figures/animation/EC.eps}

@@

  \vfill
  Gray: Observed.\\
  White: Latent.\\
  Boxed (plate): Repeated.\\

\end{frame}
\begin{frame}[t]{DSL learning as \alert{amortized} Bayesian inference}
  \includegraphics[width = 11cm]{figures/animation/DC.eps}

  \vfill
  Recognition model: Neural net.\\
  Red: Bottom-up inference.\\
  Gray: Observed.\\
  White: Latent.\\
  Boxed (plate): Repeated.\\

\end{frame}
\begin{frame}[t]{Wake: Problem solving}
  \includegraphics[width = 11cm]{figures/animation/Wake.eps}

    \vfill
  Recognition model: Neural net.\\
  Red: Bottom-up inference.\\
  Gray: Observed.\\
  White: Latent.\\
  Boxed (plate): Repeated.\\

\end{frame}
\begin{frame}[t]{Sleep-G: Memory consolidation}
  \includegraphics[width = 11cm]{figures/animation/Sleep-G.eps}
  \vfill
  \textbf{Fragment Grammars: O'Donnell 2015.}\\
  Orange: Code fragments.\\
  %% Gray: Observed.\\
  %% White: Latent.\\
  %% Boxed (plate): Repeated.\\

\end{frame}
\begin{frame}[t]{Sleep-R: Experience replay}
  \includegraphics[width = 11cm]{figures/animation/Sleep-R-1.eps}
\end{frame}
\begin{frame}[t]{Sleep-R: Dreaming}
  \includegraphics[width = 11cm]{figures/animation/Sleep-R-2.eps}
